An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state

### 2019-06-14 Manuscript revise 20190612.tex
33

\documentclass{article}
%\documentclass[review]{elsarticle}
\usepackage{amssymb,lineno}
\modulolinenumbers[5]
\usepackage{color}
\usepackage{authblk}
\usepackage{graphics}
\usepackage{mathrsfs}
\usepackage{amsmath,bm}
\usepackage{subfigure}
%\usepackage{caption,subcaption}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{setspace}
\graphicspath{{TikzFig/}{Picture/}}
\usepackage{hyperref}
%\usepackage{stackengine}
\usepackage[demo]{graphicx}
\usepackage[margin=2.5cm]{geometry}
\intextsep=8pt plus 3pt minus 1pt
\definecolor{ColorMark}{rgb}{1,1,1}
\numberwithin{equation}{section}
\numberwithin{table}{section}
\bibliographystyle{elsarticle-num}
\begin{document}

@@

\begin{table}
  \centering
  \caption{The condition of  cases classification.}
  \begin{tabular}{c|cccc}
	\toprule
	Conditions & $|s_{xx}|<\frac{2}{3}Y_0$ and $|\hat{s}_{xx}|<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$  and  $|\hat{s}_{xx}| \geq \frac{2}{3}Y_0$&  other\\
  \midrule
  $\hat{\rho^*} <\rho$ & case a: $R^{E}$ & case b: $ R^{P}$ & case c: $R^{E}R^{P}$ \\
  $\hat{\rho^*} >\rho$ & case d: $S^{E}$ & case e: $ S^{P}$ & case f: $S^{E}S^{P}$ \\
  %\hline
  \bottomrule
\end{tabular}
\label{tab:cases}
\end{table}

@@

\section*{Acknowledgement}
This work was supported by NSFC(Grant No. 11672047) and Science Challenge Project (Grant No. TZ2016002).

@@

>>>>

\documentclass{article}
%\documentclass[review]{elsarticle}
\usepackage{amssymb,lineno}
\modulolinenumbers[5]
\usepackage{color}
\usepackage{authblk}
\usepackage{graphics}
\usepackage{mathrsfs}
\usepackage{amsmath,bm}
\usepackage{subfigure}
%\usepackage{caption,subcaption}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{appendix}
\usepackage{setspace}
\graphicspath{{TikzFig/}{Picture/}}
\usepackage{hyperref}
%\usepackage{stackengine}
\usepackage{multirow}
\usepackage[demo]{graphicx}
\usepackage[margin=2.5cm]{geometry}
\intextsep=8pt plus 3pt minus 1pt
\definecolor{ColorMark}{rgb}{1,1,1}
\numberwithin{equation}{section}
\numberwithin{table}{section}
\bibliographystyle{elsarticle-num}
\begin{document}

@@

\begin{table}
  \centering
  \caption{The condition of  cases classification.}
  \begin{tabular}{c|ccc}
	\toprule
	\multirow{2}{*}{  $\hat{\rho^*} <\rho$ }  &  $\hat{s}_{xx}<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$ and  $\hat{s}_{xx} \geq \frac{2}{3}Y_0$ &  other\\
 & case a: $R^{E}$ & case b: $ R^{P}$ & case c: $R^{E}R^{P}$ \\
 \hline
 \multirow{2}{*}{  $\hat{\rho^*} >\rho$ } & $\hat{s}_{xx} > -\frac{2}{3}Y_0$ & $s_{xx}=-\frac{2}{3}Y_0$  and  $\hat{s}_{xx} \leq -\frac{2}{3}Y_0$&  other\\
  & case d: $S^{E}$ & case e: $ S^{P}$ & case f: $S^{E}S^{P}$ \\
  %\hline
  \bottomrule
\end{tabular}
\label{tab:cases}
\end{table}

@@

\section*{Acknowledgement}r
This work was supported by NSFC(Grant No. 11672047) and Science Challenge Project (Grant No. TZ2016002).

@@

  \section{Gauss-Legendre  quadrature}
  In this paper, we use Gauss-Legendre quadrature to  take  numerical integrations. 
For a function $f(x)$,  the intergration from $-1$ to $1$ is given as
$$ 
  \int_{-1}^1 f(x)dx \approx \sum_{i=0}^n \omega_i f(x_i)
$$
$\omega_i$ is the weight, and $x_i$ is the integrating point.
For different orders they are listed in Table \ref{tab:coe}.

\subsection{}
\begin{table}\label{tab:coe}
  \centering
  \caption{Coefficiences for Guass-Legendere quadrature}
  \begin{tabular}{cccc}
	\toprule
	Number of points, $n$ &  Order & Points, $x_i$ & Weights, $\omega_i$ \\
	\midrule
	1 & 1  & 0 & 2 \\
	\hline
	2 & 3  & $\pm \frac{1}{\sqrt{3}}$ & 1 \\
	\hline
	\multirow{4}{*}{3} &\multirow{4}{*}{3} & 0  & $\frac{8}{9}$ \\
	\cline{3-4}
	& & $\pm\sqrt{\frac{3}{5}}$ & $\frac{5}{9} $\\
	\hline
	\multirow{4}{*}{\makecell{4}} & \multirow{4}{*}{7}  & $\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18+\sqrt{30}}{36}$ \\
	\cline{3-4}
  &  &  $\pm \sqrt{\frac{3}{7} +\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18-\sqrt{30}}{36}$ \\
  \bottomrule
\end{tabular}
\end{table}
